CS6213 Project Report

### 2021-05-07 report/paper.tex
WIP

\section{Approach}

@@

\subsection{Takeaways}

>>>>

\section{TLA Specification}

\subsection{Experience with Apalache}

\subsection{Constraining TLC's Search Space}

We found four ways to cut down the state space in TLC:

\begin{itemize}
    \item \textbf{State constraints.} If the predicate does not hold for a state, TLC does not explore any of its successors.

    \item \textbf{Symmetry}. Two states are considered equal if they are permutations of another with reference to a symmetry set.

    \item \textbf{Action constraints}. Similar to state constraints, but refer to primed variables.
    %
    They are used to eliminate possible actions.

    \item \textbf{Views}. Provide a way to change when TLC considers two states to be equal---two states are equal if their view evaluates to to the same value.
    %
    We use a view to instruct TLC to ignore history variables when comparing states, which leads to a 2 orders of magnitude reduction in the number of states explored.

\section{Testing Approach}

@@

\section{Takeaways}
